working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
intro

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
predict and show a greater negative effect of closely related species
Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
studies however, have focused on the impacts of heterospecific pollen on
fitness of distantly related species Galen and Gregory (1989); Neiland
and Wilcock (1999). Yet, most insects and most stigmas have been found
to carry multiple species of foreign pollen with little attention to
degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
(2013). The relative amounts of closely/far related pollen that arrives
to a stigma gives a first snapshoot where pollen competition can occur
and improves the understanding of how important the reduction of fitness
can be from heterospecific pollen where closely related species cand
lead to greater detrimental effects Arceo-Gómez and Ashman (2016).

>>>>

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
predict and show a greater negative effect of closely related species
Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
studies however, have focused on the impacts of heterospecific pollen on
fitness of distantly related species Galen and Gregory (1989); Neiland
and Wilcock (1999). Despite the fact that far related species are also
able to decrease species fitness (REFS). Yet, most insects and most
stigmas have been found to carry multiple species of foreign pollen with
little attention to degree of relatedness (Arceo-Gómez and Ashman
(2016); Fang and Huang (2013). The relatedness of foreign pollen gives a
first snapshoot of where the pollen competition can occur and therefore
could be a proxy of effect. With that said, Arceo-Gómez and Ashman
(2016) is the only work which has proven a greater effect of far and
close related pollen with published data with low sample sizes and lack
of significance.
